Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-09-06 3dpas_intro.tex
removing alpha and beta

In \S\ref{sec:distdyndata} we characterized dynamic and distributed
properties of the D3 Science applications. Our analysis was
qualitative by necessity, due to the fact that approaches to quantify
dynamism and distributed properties were often intimately tied to
application/scenario definition and specific usage modes.
Notwithstanding, to quantify better dynamic properties of an
application, we believe a term analogous to the use of Amdahl's
number~\cite{10.1109/ICDE.2000.839382}, such as $\alpha$ defined as Number\ of
Compute\ Operation / Amount\ Data (Consumed,\ Generated\ or\ Transformed)
% \begin{itemize}
% \item[] Num. of Compute Operations / Amount of Data
%   (Consumed, Generated or Transformed)
% \end{itemize}
could be used to characterize `static' data-intensive applications and systems.
%\begin{itemize}
%\item[] $\alpha$ = Num. of Compute Operations / Amount of Data
%  (Consumed, Generated or Transformed)
%\end{itemize}
Note that this term is scale-invariant, i.e., a value of 1 could
correspond to very small or very large values of both numerator and
denominator, and that it does not capture the time scales over
which data changes.

@@

Similarly, another term $\beta$ defined as Amount of Data Transferred / Degree of Distribution
% \begin{itemize}
% \item[] Amount of Data Transferred / Degree of
%   Distribution
% \end{itemize}
could be used to quantify the
``scale'' of distribution, namely the degree of distribution as a
function of the amount of data transferred, where the degree of
distribution can be defined as the number of distinct data locations.

>>>>

In \S\ref{sec:distdyndata} we characterized dynamic and distributed
properties of the D3 Science applications. Our analysis was
qualitative by necessity, due to the fact that approaches to quantify
dynamism and distributed properties were often intimately tied to
application/scenario definition and specific usage modes.
Notwithstanding, to quantify better dynamic properties of an
application, we believe a term analogous to the use of Amdahl's
number~\cite{10.1109/ICDE.2000.839382}, such as [Number\ of
Compute\ Operation / Amount\ Data (Consumed,\ Generated\ or\ Transformed)]
% \begin{itemize}
% \item[] Num. of Compute Operations / Amount of Data
%   (Consumed, Generated or Transformed)
% \end{itemize}
could be used to characterize `static' data-intensive applications and systems.
%\begin{itemize}
%\item[] $\alpha$ = Num. of Compute Operations / Amount of Data
%  (Consumed, Generated or Transformed)
%\end{itemize}
Note that this term is scale-invariant, i.e., a value of 1 could
correspond to very small or very large values of both numerator and
denominator, and that it does not capture the time scales over
which data changes.

@@

Similarly, another term [Amount of Data Transferred / Degree of Distribution]
% \begin{itemize}
% \item[] Amount of Data Transferred / Degree of
%   Distribution
% \end{itemize}
could be used to quantify the
``scale'' of distribution, namely the degree of distribution as a
function of the amount of data transferred, where the degree of
distribution can be defined as the number of distinct data locations.
